Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-12-16 ijar-npb-ms.tex
slight rework of sec1 and sec2

(some sentences may be useful for the abstract)

@@

The survival signature allows for straightforward computation of system reliability
for systems with complex layouts and multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components,
by partitioning the event $\Tsys > t$ according to the number of components of type $k$ functioning at time $t$,
denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$, and applying the law of total probability:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align*}

@@

The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}. 
There are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
\end{align}

Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
Then, for system failure time $\Tsys$,
\begin{align*}
P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}

@@

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
***This step is less trivial here as we must ensure to have probability distributions for these events,
thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
***covered because of parametric distribution, min and max over parameter sets (see section 6)***
***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
to reflect uncertainty about system functioning for known states of its components.
A further suggestion was to generalize this to lower and upper structure functions,
within the theory of imprecise probability \citep{itip,CU11}.
These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
which in the latter case also becomes an imprecise probability.

@@

\section{Nonparametric Bayesian Approach}

>>>>

(some sentences may be useful for the abstract instead)

@@

The survival signature allows for straightforward computation of system reliability
for systems with complex layouts and multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components,
by partitioning the event $\Tsys > t$ according to the number of components of each type functioning at time $t$.

@@

The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}.
Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$, such that $\Rsys(t) = P(\Tsys > t)$
can be calculated using the law of total probability:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \\
 &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \,,
%                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align*}
where $C^k_t \in \{0, 1, \ldots, m_k\}$ denotes
the random number of components of type $k$ functioning at time $t$.

For calculating the survival signature based on the structure function, observe that
there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
\end{align}
%
%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
%Then, for system failure time $\Tsys$,
%\begin{align*}
%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
%\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}
We will employ both assumptions in this paper,
such that $C^k_t$ is Beta-Binomially distributed,
giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.

@@

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
***This step is less trivial here as we must ensure to have probability distributions for these events,
thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
***covered because of parametric distribution, min and max over parameter sets (see section 6)***
***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
\td{Leave out the sentences framed with `***'?}
Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
to reflect uncertainty about system functioning for known states of its components.
A further suggestion was to generalize this to lower and upper structure functions,
within the theory of imprecise probability \citep{itip,CU11}.
These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
which in the latter case also becomes an imprecise probability.

@@

\section{Nonparametric Bayesian Approach for Component Reliability}
